\documentclass[11pt, letterpaper]{article}

% --- Packages ---
\usepackage[margin=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{palatino}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% --- Colors ---
\definecolor{heading}{HTML}{1a5276}

% --- Section formatting ---
\titleformat{\section}{\large\bfseries\color{heading}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.2em}{0.6em}

% --- List formatting ---
\setlist[itemize]{left=0pt, nosep, label={}}

% --- Commands ---
\newcommand{\cventry}[4]{%
  \noindent\textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4} \\[0.4em]
}

\newcommand{\cvpub}[1]{\noindent #1 \\[0.4em]}

% --- TODO marker (renders as highlighted box in PDF, edit cv/cv.tex to resolve) ---
\newcommand{\cvtodo}[1]{%
  \noindent\fcolorbox{orange}{yellow!20}{%
    \parbox{\dimexpr\textwidth-2\fboxsep-2\fboxrule}{%
      \small\textbf{TODO} \textit{(edit \texttt{cv/cv.tex}):} #1%
    }%
  }\\[0.6em]%
}

% --- Document ---
\begin{document}

\begin{center}
  {\LARGE\bfseries Chan-Ye (Chris) Ohh} \\[0.3em]
  Postdoctoral Scholar, Marine Physical Laboratory, Scripps Institution of Oceanography \\
  \href{mailto:cohh@ucsd.edu}{cohh@ucsd.edu} \quad
  \href{https://orcid.org/0000-0002-7313-4291}{ORCID: 0000-0002-7313-4291} \\
  \href{https://scholar.google.com/citations?user=3VvK59oAAAAJ}{Google Scholar}
\end{center}

\section{Education}

\cventry{University of Southern California}{Los Angeles, CA}{Ph.D., Mechanical Engineering}{2017--2023}

\cventry{University of Southern California}{Los Angeles, CA}{M.S., Mechanical Engineering}{2015--2017}

\cvtodo{Add B.S. degree if applicable.}

\section{Research Experience}

\cventry{Postdoctoral Scholar}{La Jolla, CA}
  {Air-Sea Interaction Laboratory, Scripps Institution of Oceanography, UC San Diego}{2025--Present}

\cventry{Postdoctoral Scholar}{Seattle, WA}
  {Applied Physics Laboratory, University of Washington}{2023--2025}

\cventry{Graduate Research Assistant}{Los Angeles, CA}
  {Stratified Fluids Laboratory, University of Southern California}{2017--2023}

\section{Publications}

\cvpub{%
  \textbf{C.-Y. Ohh} and G.\,R. Spedding (2024).
  ``The effects of stratification on the near wake of 6:1 prolate spheroid.''
  \textit{Journal of Fluid Mechanics}, 997, A43.
  \href{https://doi.org/10.1017/jfm.2024.829}{doi:10.1017/jfm.2024.829}.
  \textit{Open Access (CC BY 4.0).}
}

\cvpub{%
  \textbf{C.-Y. Ohh} and G.\,R. Spedding (2022).
  ``Wake identification of stratified flows using dynamic mode decomposition.''
  \textit{Physical Review Fluids}, 7, 024801.
  \href{https://doi.org/10.1103/PhysRevFluids.7.024801}{doi:10.1103/PhysRevFluids.7.024801}.
  \textit{Editor's Suggestion.}
}

\cvpub{%
  V.\,K. Chinta, \textbf{C.-Y. Ohh}, G. Spedding, and M. Luhar (2022).
  ``Regime identification for stratified wakes from limited measurements:
    a library-based sparse regression formulation.''
  \textit{Physical Review Fluids}, 7, 033803.
  \href{https://doi.org/10.1103/PhysRevFluids.7.033803}{doi:10.1103/PhysRevFluids.7.033803}.
}

\cvtodo{Add any additional publications not listed above.}

\section{Presentations}

\cvpub{%
  \textbf{C.-Y. Ohh}, M. Oliver, and G.\,R. Spedding (2023).
  ``The near-wake of an inclined 6:1 prolate spheroid in a stratified fluid.''
  APS Division of Fluid Dynamics Meeting (DFD23), Washington, DC. \textit{(Oral)}
}

\cvpub{%
  \textbf{C.-Y. Ohh}, M. Oliver, and G.\,R. Spedding (2022).
  ``Asymmetric stratified wakes.''
  APS Division of Fluid Dynamics Meeting (DFD22), Indianapolis, IN. \textit{(Oral)}
}

\cvpub{%
  V.\,K. Chinta, M. Jones, M. Yee, P. Loekman, \textbf{C.-Y. Ohh}, G.\,R. Spedding, and M. Luhar (2021).
  ``Regime classification for stratified wakes from planar velocity field snapshots
    using convolutional neural networks.''
  APS Division of Fluid Dynamics Meeting (DFD21), Phoenix, AZ. \textit{(Poster)}
}

\cvpub{%
  \textbf{C.-Y. Ohh} and G.\,R. Spedding (2019).
  ``Wake identification of stratified flows using Dynamic Mode Decomposition.''
  APS Division of Fluid Dynamics Meeting (DFD19), Seattle, WA. \textit{(Oral)}
}

\cvpub{%
  \textbf{C.-Y. Ohh}, Y. Huang, Z. Wen, E. Kanso, and M. Luhar (2016).
  ``Leveraging fluid-structure interaction for passive control of flapping locomotion.''
  APS Division of Fluid Dynamics Meeting (DFD16), Portland, OR. \textit{(Oral)}
}

\cvtodo{Verify this list is complete and add any invited seminars or additional presentations.}

\section{Awards \& Honors}

\noindent Poster Award (Second Place), APS Division of Fluid Dynamics Meeting \hfill 2021 \\[0.4em]

\cvtodo{Add any additional awards, fellowships, or honors.}

\cvtodo{Add additional sections as needed: Teaching, Service \& Outreach, Skills.}

\end{document}
